---
title: "absent_GSC_gene_interaction_network_sorting"
author: "Luke"
date: "2023-07-05"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(knitr)
library(dslabs)
library(dplyr)
library("writexl")
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.



```{r}
data1 <- read.csv('/Users/la424/Documents/Ortholog FBGN numbers across species.csv')
head(data1)

```

```{r}
data1_sim <- select(data1, simulans) 
data1_sec <- select(data1, sechelia)
data1_tei <- select(data1, teissieri)
data1_yak <- select(data1, yakuba)
data1_tak <- select(data1, takahashii)
data1_ele <- select(data1, elegans)
data1_ser <- select(data1, serrata)
data1_ana <- select(data1, ananassae)
data1_pse <- select(data1, pseudoobscura)
data1_obs <- select(data1, obscura)
data1_wil <- select(data1, willistoni)
data1_moj <- select(data1, mojavensis)
data1_vir <- select(data1, virilis)
data1_gri <- select(data1, grimshawi)
data1_rub <- select(data1, rubida)
data1_dom <- select(data1, domestica)
data1_cup <- select(data1, cuprina)
```


```{r}
data1_sim2 <- data1_sim$Here <- "yes"
data1_sec2 <- data1_sec$Here <- "yes"
data1_tei2 <- data1_tei$Here <- "yes"
data1_yak2 <- data1_yak$Here <- "yes"
data1_tak2 <- data1_tak$Here <- "yes"
data1_ele2 <- data1_ele$Here <- "yes"
data1_ser2 <- data1_ser$Here <- "yes"
data1_ana2 <- data1_ana$Here <- "yes"
data1_pse2 <- data1_pse$Here <- "yes"
data1_obs2 <- data1_obs$Here <- "yes"
data1_wil2 <- data1_wil$Here <- "yes"
data1_moj2 <- data1_moj$Here <- "yes"
data1_vir2 <- data1_vir$Here <- "yes"
data1_gri2 <- data1_gri$Here <- "yes"
data1_rub2 <- data1_rub$Here <- "yes"
data1_dom2 <- data1_dom$Here <- "yes"
data1_cup2 <- data1_cup$Here <- "yes"

```

```{r}
head(data1_sim)
```





```{r}
data2 <- read.csv('/Users/la424/Documents/gene_symbol_and_FBgn_absent_interactions.csv')
head(data2)

```
```{r}
data3 <- read.csv('/Users/la424/Documents/gene_symbol_and_FBgn_absent_interactons_simple.csv')
head(data3)
```

```{r}

q_2a <- left_join(data2, data1_sim, by = c('FBgn'='simulans')) %>% 
  write_xlsx('/Users/la424/Documents/sim_absences1.xlsx')
  
```

```{r}
write_xlsx(q_2a, '/Users/la424/Documents/sim_absences.xlsx')
```



```{r}
q_3a <- left_join(data3, data1_sec, by = c('FBgn'='sechelia')) %>% 
  write_xlsx('/Users/la424/Documents/sec_absences.xlsx')
```

```{r}
q_4a <- left_join(data3, data1_tei, by = c('FBgn'='teissieri')) %>% 
  write_xlsx('/Users/la424/Documents/tei_absences.xlsx')
```

```{r}
q_5a <- left_join(data3, data1_yak, by = c('FBgn'='yakuba')) %>% 
  write_xlsx('/Users/la424/Documents/yak_absences.xlsx')
```

```{r}
q_6a <- left_join(data3, data1_tak, by = c('FBgn'='takahashii')) %>% 
  write_xlsx('/Users/la424/Documents/tak_absences.xlsx')
q_7a <- left_join(data3, data1_ele, by = c('FBgn'='elegans')) %>% 
  write_xlsx('/Users/la424/Documents/ele_absences.xlsx')
```


```{r}
q_8a <- left_join(data3, data1_ser, by = c('FBgn'='serrata')) %>% 
  write_xlsx('/Users/la424/Documents/ser_absences.xlsx')
q_9a <- left_join(data3, data1_ana, by = c('FBgn'='ananassae')) %>% 
  write_xlsx('/Users/la424/Documents/ana_absences.xlsx')
q_10a <- left_join(data3, data1_pse, by = c('FBgn'='pseudoobscura')) %>% 
  write_xlsx('/Users/la424/Documents/pse_absences.xlsx')
q_11a <- left_join(data3, data1_obs, by = c('FBgn'='obscura')) %>% 
  write_xlsx('/Users/la424/Documents/obs_absences.xlsx')
q_12a <- left_join(data3, data1_wil, by = c('FBgn'='willistoni')) %>% 
  write_xlsx('/Users/la424/Documents/wil_absences.xlsx')
q_13a <- left_join(data3, data1_moj, by = c('FBgn'='mojavensis')) %>% 
  write_xlsx('/Users/la424/Documents/moj_absences.xlsx')
q_14a <- left_join(data3, data1_vir, by = c('FBgn'='virilis')) %>% 
  write_xlsx('/Users/la424/Documents/vir_absences.xlsx')
q_15a <- left_join(data3, data1_gri, by = c('FBgn'='grimshawi')) %>% 
  write_xlsx('/Users/la424/Documents/gri_absences.xlsx')
q_16a <- left_join(data3, data1_rub, by = c('FBgn'='rubida')) %>% 
  write_xlsx('/Users/la424/Documents/rub_absences.xlsx')
q_17a <- left_join(data3, data1_dom, by = c('FBgn'='domestica')) %>% 
  write_xlsx('/Users/la424/Documents/dom_absences.xlsx')
q_18a <- left_join(data3, data1_cup, by = c('FBgn'='cuprina')) %>% 
  write_xlsx('/Users/la424/Documents/cup_absences.xlsx')

```








```{r}
data4 <- read.csv('/Users/la424/Documents/genes_that_disappeared.csv')
head(data4)
```

```{r}
q_2a <- left_join(data4, data1_sim, by = c('FBgn'='simulans')) %>% 
  write_xlsx('/Users/la424/Documents/sim_absences2.xlsx')
q_3a <- left_join(data4, data1_sec, by = c('FBgn'='sechelia')) %>% 
  write_xlsx('/Users/la424/Documents/sec_absences2.xlsx')
q_4a <- left_join(data4, data1_tei, by = c('FBgn'='teissieri')) %>% 
  write_xlsx('/Users/la424/Documents/tei_absences2.xlsx')
q_5a <- left_join(data4, data1_yak, by = c('FBgn'='yakuba')) %>% 
  write_xlsx('/Users/la424/Documents/yak_absences2.xlsx')
q_6a <- left_join(data4, data1_tak, by = c('FBgn'='takahashii')) %>% 
  write_xlsx('/Users/la424/Documents/tak_absences2.xlsx')
q_7a <- left_join(data4, data1_ele, by = c('FBgn'='elegans')) %>% 
  write_xlsx('/Users/la424/Documents/ele_absences2.xlsx')
q_8a <- left_join(data4, data1_ser, by = c('FBgn'='serrata')) %>% 
  write_xlsx('/Users/la424/Documents/ser_absences2.xlsx')
q_9a <- left_join(data4, data1_ana, by = c('FBgn'='ananassae')) %>% 
  write_xlsx('/Users/la424/Documents/ana_absences2.xlsx')
q_10a <- left_join(data4, data1_pse, by = c('FBgn'='pseudoobscura')) %>% 
  write_xlsx('/Users/la424/Documents/pse_absences2.xlsx')
q_11a <- left_join(data4, data1_obs, by = c('FBgn'='obscura')) %>% 
  write_xlsx('/Users/la424/Documents/obs_absences2.xlsx')
q_12a <- left_join(data4, data1_wil, by = c('FBgn'='willistoni')) %>% 
  write_xlsx('/Users/la424/Documents/wil_absences2.xlsx')
q_13a <- left_join(data4, data1_moj, by = c('FBgn'='mojavensis')) %>% 
  write_xlsx('/Users/la424/Documents/moj_absences2.xlsx')
q_14a <- left_join(data4, data1_vir, by = c('FBgn'='virilis')) %>% 
  write_xlsx('/Users/la424/Documents/vir_absences2.xlsx')
q_15a <- left_join(data4, data1_gri, by = c('FBgn'='grimshawi')) %>% 
  write_xlsx('/Users/la424/Documents/gri_absences2.xlsx')
q_16a <- left_join(data4, data1_rub, by = c('FBgn'='rubida')) %>% 
  write_xlsx('/Users/la424/Documents/rub_absences2.xlsx')
q_17a <- left_join(data4, data1_dom, by = c('FBgn'='domestica')) %>% 
  write_xlsx('/Users/la424/Documents/dom_absences2.xlsx')
q_18a <- left_join(data4, data1_cup, by = c('FBgn'='cuprina')) %>% 
  write_xlsx('/Users/la424/Documents/cup_absences2.xlsx')
```


```{r}
data5 <- read.csv('/Users/la424/Documents/genes_that_disappeared_2.csv')
head(data4)
```

```{r}
q_2a <- left_join(data5, data1_sim, by = c('FBgn'='simulans')) %>% 
  write_xlsx('/Users/la424/Documents/sim_absences3.xlsx')
q_3a <- left_join(data5, data1_sec, by = c('FBgn'='sechelia')) %>% 
  write_xlsx('/Users/la424/Documents/sec_absences3.xlsx')
q_4a <- left_join(data5, data1_tei, by = c('FBgn'='teissieri')) %>% 
  write_xlsx('/Users/la424/Documents/tei_absences3.xlsx')
q_5a <- left_join(data5, data1_yak, by = c('FBgn'='yakuba')) %>% 
  write_xlsx('/Users/la424/Documents/yak_absences3.xlsx')
q_6a <- left_join(data5, data1_tak, by = c('FBgn'='takahashii')) %>% 
  write_xlsx('/Users/la424/Documents/tak_absences3.xlsx')
q_7a <- left_join(data5, data1_ele, by = c('FBgn'='elegans')) %>% 
  write_xlsx('/Users/la424/Documents/ele_absences3.xlsx')
q_8a <- left_join(data5, data1_ser, by = c('FBgn'='serrata')) %>% 
  write_xlsx('/Users/la424/Documents/ser_absences3.xlsx')
q_9a <- left_join(data5, data1_ana, by = c('FBgn'='ananassae')) %>% 
  write_xlsx('/Users/la424/Documents/ana_absences3.xlsx')
q_10a <- left_join(data5, data1_pse, by = c('FBgn'='pseudoobscura')) %>% 
  write_xlsx('/Users/la424/Documents/pse_absences3.xlsx')
q_11a <- left_join(data5, data1_obs, by = c('FBgn'='obscura')) %>% 
  write_xlsx('/Users/la424/Documents/obs_absences3.xlsx')
q_12a <- left_join(data5, data1_wil, by = c('FBgn'='willistoni')) %>% 
  write_xlsx('/Users/la424/Documents/wil_absences3.xlsx')
q_13a <- left_join(data5, data1_moj, by = c('FBgn'='mojavensis')) %>% 
  write_xlsx('/Users/la424/Documents/moj_absences3.xlsx')
q_14a <- left_join(data5, data1_vir, by = c('FBgn'='virilis')) %>% 
  write_xlsx('/Users/la424/Documents/vir_absences3.xlsx')
q_15a <- left_join(data5, data1_gri, by = c('FBgn'='grimshawi')) %>% 
  write_xlsx('/Users/la424/Documents/gri_absences3.xlsx')
q_16a <- left_join(data5, data1_rub, by = c('FBgn'='rubida')) %>% 
  write_xlsx('/Users/la424/Documents/rub_absences3.xlsx')
q_17a <- left_join(data5, data1_dom, by = c('FBgn'='domestica')) %>% 
  write_xlsx('/Users/la424/Documents/dom_absences3.xlsx')
q_18a <- left_join(data5, data1_cup, by = c('FBgn'='cuprina')) %>% 
  write_xlsx('/Users/la424/Documents/cup_absences3.xlsx')
```

```{r}
q_14a <- left_join(data5, data1_vir, by = c('FBgn'='virilis')) %>% 
  write_xlsx('/Users/la424/Documents/vir_absences3.xlsx')
```

```{r}
data6 <- read.csv('/Users/la424/Documents/Bam_interacting_genes_remaining.csv')
head(data6)
```

```{r}
q__2a <- left_join(data6, data1_sim, by = c('FBgn'='simulans')) %>% 
  write_xlsx('/Users/la424/Documents/sim_absences_bam.xlsx')
q__3a <- left_join(data6, data1_sec, by = c('FBgn'='sechelia')) %>% 
  write_xlsx('/Users/la424/Documents/sec_absences_bam.xlsx')
q__4a <- left_join(data6, data1_tei, by = c('FBgn'='teissieri')) %>% 
  write_xlsx('/Users/la424/Documents/tei_absences_bam.xlsx')
q__5a <- left_join(data6, data1_yak, by = c('FBgn'='yakuba')) %>% 
  write_xlsx('/Users/la424/Documents/yak_absences_bam.xlsx')
q__6a <- left_join(data6, data1_tak, by = c('FBgn'='takahashii')) %>% 
  write_xlsx('/Users/la424/Documents/tak_absences_bam.xlsx')
q__7a <- left_join(data6, data1_ele, by = c('FBgn'='elegans')) %>% 
  write_xlsx('/Users/la424/Documents/ele_absences_bam.xlsx')
q__8a <- left_join(data6, data1_ser, by = c('FBgn'='serrata')) %>% 
  write_xlsx('/Users/la424/Documents/ser_absences_bam.xlsx')
q__9a <- left_join(data6, data1_ana, by = c('FBgn'='ananassae')) %>% 
  write_xlsx('/Users/la424/Documents/ana_absences_bam.xlsx')
q__10a <- left_join(data6, data1_pse, by = c('FBgn'='pseudoobscura')) %>% 
  write_xlsx('/Users/la424/Documents/pse_absences_bam.xlsx')
q__11a <- left_join(data6, data1_obs, by = c('FBgn'='obscura')) %>% 
  write_xlsx('/Users/la424/Documents/obs_absences_bam.xlsx')
q__12a <- left_join(data6, data1_wil, by = c('FBgn'='willistoni')) %>% 
  write_xlsx('/Users/la424/Documents/wil_absences_bam.xlsx')
q__13a <- left_join(data6, data1_moj, by = c('FBgn'='mojavensis')) %>% 
  write_xlsx('/Users/la424/Documents/moj_absences_bam.xlsx')
q__14a <- left_join(data6, data1_vir, by = c('FBgn'='virilis')) %>% 
  write_xlsx('/Users/la424/Documents/vir_absences_bam.xlsx')
q__15a <- left_join(data6, data1_gri, by = c('FBgn'='grimshawi')) %>% 
  write_xlsx('/Users/la424/Documents/gri_absences_bam.xlsx')
q__16a <- left_join(data6, data1_rub, by = c('FBgn'='rubida')) %>% 
  write_xlsx('/Users/la424/Documents/rub_absences_bam.xlsx')
q__17a <- left_join(data6, data1_dom, by = c('FBgn'='domestica')) %>% 
  write_xlsx('/Users/la424/Documents/dom_absences_bam.xlsx')
q__18a <- left_join(data6, data1_cup, by = c('FBgn'='cuprina')) %>% 
  write_xlsx('/Users/la424/Documents/cup_absences_bam.xlsx')
```

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

